---
title: "Summative Assessment 2"
author: "Vera Frances A. Aguila"
date: "2024-12-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This performs the necessary assumption checks for conducting a 2-Factor ANOVA on the Alzheimer's Mice Data. Assumptions include normality, homogeneity of variance, and independence of observations.


```{r }
# Load required libraries
library(tidyverse)
library(car)

# Load the data
data <- read.csv("Alzheimers Mice Data.csv")

# View the first few rows
head(data)

```


##Check Assumptions

###Assumption 1: Normality
The Shapiro-Wilk test is used to check normality for the Training and Memory columns. Histograms with density curves and QQ plots are also generated for visual inspection.

```{r }
# Normality check
training_normality <- shapiro.test(data$Training)
memory_normality <- shapiro.test(data$Memory)

# Display results
training_normality
memory_normality

# Visual inspection: histograms
par(mfrow = c(1, 2)) # Set layout
hist(data$Training, breaks = 10, col = "blue", main = "Training Errors", xlab = "Errors")
lines(density(data$Training), col = "red")

hist(data$Memory, breaks = 10, col = "green", main = "Memory Errors", xlab = "Errors")
lines(density(data$Memory), col = "red")


```

### Assumption 2: Homogeneity of Variance
Levene's test is performed to assess homogeneity of variances.


```{r }
# Levene's Test for Training Errors
levene_training <- leveneTest(Training ~ as.factor(AD_Status) * as.factor(Treatment), data = data)
levene_training

# Levene's Test for Memory Errors
levene_memory <- leveneTest(Memory ~ as.factor(AD_Status) * as.factor(Treatment), data = data)
levene_memory


```

##Results


```{r }


```





